### 2020-02-02 docs/input.tex
trunk 0.6.6 removed stray output in physics
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@3151 40876441-3496-0410-a613-a2fca35b2ae2

\subsubsection{Liquid crystal anshoring}

@@

\subsection{Porous media}

Porous media calculations can be undertaken when appropriate
solid/fluid status information is supplied. The are a number
of switches available in the input file:
\begin{lstlisting}
porous_media_file
porous_media_format
porous_media_type
\end{lstlisting}

specifies the file stub name to be read at the start of execution.
(If the stub name is \texttt{file} then the code will expect to
find \texttt{file.001-001} in the current directory.

is either \texttt{ASCII} or \texttt{BINARY} as appropriate. Note that
in parallel, a single data file can be supplied, but it must be binary.
The default is \texttt{BINARY}.

is either \texttt{status\_only} (the default) or \texttt{status\_with\_h}.

\subsubsection{File format}

In all cases the status (fluid/solid) information is represented by a
single \texttt{char} (or integer), which must be supplied via the
porous media file. A single file should contain data matching the
current system size, and have the $z-$direction running fastest,
followed by the $y-$direction. Note that in non-periodic directions,
the structure must be 'closed', i.e., all the points at the edge
should be solid.

Fluid sites are designated by \texttt{0} and boundary or solid sites
by \texttt{1}. These data should be of type \texttt{char} in binary,
and may be integer in ASCII.

Where wetting information is required, the free energy parameter $H$
can be supplied by using the \texttt{status\_with\_h} switch. In this
case, the \texttt{char} status is augmented by a single \texttt{double}
value which is the local value of $H$. The order is then
$s_1,h_1, s_2, h_2, \ldots$.

An example of how to construct a porous media file is provided in
\texttt{util/capillary.c}, which builds an appropriate file for
a square or circular capillary tube. Please see the comments in
the file for further details. Note that the allowed
solid/fluid status values are defined in \texttt{src/site\_map.h}.
A solid boundary is \texttt{BOUNDARY}, while fluid is \texttt{FLUID}.

>>>>

\subsubsection{Liquid crystal anchoring}

@@
